\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mhchem}

\title{Thermochemistry Notes}
\author{Sai Nallani}

\begin{document}
\maketitle

\section{Vocabulary}
\begin{enumerate}
    \item The \textbf{system} is the part of the universe that we are studying.
    \item The \textbf{surroundings} are everything else in the universe.
    \item The \textbf{universe} consists of the system and the surroundings.
\end{enumerate}
\section{Laws}
\begin{enumerate}
    \item The \textbf{1st law of thermodynamics} is $\mathbf{\Delta{E} = q + w}$.
    \begin{enumerate}
        \item $\mathbf{\Delta{E}}$ is the change in the internal energy of the system.
        \item The internal energy is the sum of all the kinetic and potential
        energies of the components of the system.
        \item $\mathbf{q}$ refers to the heat absorbed or released by the system.
        \begin{itemize}
            \item $\mathbf{q}$ is \textbf{positive} when heat flows \textbf{into} the system 
            \textbf{from} the surroundings and \textbf{negative} when heat flows \textbf{from} the system
            \textbf{into} the surroundings.
        \end{itemize}
        \item $\mathbf{w}$ refers to the work done on or done by the system.
            \begin{itemize}
                \item $\mathbf{w}$ is \textbf{positive} when  work is done \textbf{on} the system 
                \textbf{by} the surroundings and \textbf{negative} when work is done \textbf{by} the system
                \textbf{on} the surroundings.
            \end{itemize}
    \end{enumerate} 
\end{enumerate}
\section{Problems and Applications}
\begin{enumerate}
    \item 1st law on combustion of propane in open container at constant
    pressure.
    \begin{center}
        $\ce{C3H8 (g) + 5O2 (g) -> 3CO2 (g) + 4H2O (g)}$\\
        $q = -2044$ kJ,
        $w = -2$ kJ \\
        $\Delta{E} = q + w = (-2044) + (-2) = -2046$ kJ\\
        $q_p = \Delta{H} = -2044$ kJ
    \end{center}
\end{enumerate}
\section{Enthalpy}
An \textbf{endothermic} ($\Delta{H}$ is $+$) process is where heat is transferred to the system,
while an \textbf{exothermic} ($\Delta{H}$ is $-$) process is where heat is transferred out of 
the system. 
\end{document}